---
---

## Console

The interpreter accepts commands interactively through the console.

===

Basic math, as you would type it on a calculator, is usually a valid command in the R language:

```{r}
1 + 2
```

```{r}
4^2
```

===

Question
: Why is the output prefixed by `[1]`?

Answer
: {:.fragment} That's the index, or position in a vector, of the first result.

===

A command giving a vector of results shows this clearly:

```{r}
seq(1, 100)
```

===

The interpreter understands more than arithmatic operations.
That last command told it to use (or "call") the function `seq()`.

Most of "learning R" involves getting to know a whole lot of functions, the
effect of each function's  arguments (e.g. the input values `1` and `100`), and
what each function returns (e.g. the output vector).
{:.notes}

===

## R as Calculator

A good place to begin learning R is with its built-in mathematical functionality.

===

## Arithmatic operators

Try `+`, `-`, `*`, `/`, and `^` (for raising to a power).

```{r}
5/3
```

===

## Logical tests

Test equality with `==` and inequality with `<=`, `<`, `!=`, `>`, or `>=`.

```{r}
1/2 == 0.5
```

===

## Math functions

Common mathematical functions like `sin`, `log`, and `sqrt`, exist along side some universal constants.

```{r}
sin(2 * pi)
```

===

## Programming idoms

Common computer programming functions like 'rep', 'sort', and 'range'

```{r}
rep(2, 5)
```

===

## Parentheses

Sandwiching something with `(` and `)` has two possible meanings.

===

Group sub-expressions by parentheses where needed.

```{r}
(1 + 2) / 3
```

===

Call functions by typing their name and comma-separated arguments between parentheses.

```{r}
logb(2, 2)
```
