---
---

## Environment

In the RStudio IDE, the environment tab displays any variables added to R's
vocabulary in the current session. In a brand new session, the R interpreter
already recognizes many things, despite the environment being "empty".
{:.notes}

With an "empty" environment, the interpreter still recognizes:

- any number
- any string of characters
- nearly universal operators (e.g. `+` and `/`)
- operators specific to R (e.g. `$` and `%*%`)
- functions in "base R"

===

To reference a number or function just type it in as above.
To referece a string of characters, surround them in quotation marks.

```{r}
'ab.cd'
```

===

Without quotation marks, the interpreter checks for things in the environment
named `ab.cd` and doesn't find anything:

```{r error = TRUE}
ab.cd
```

===

Question
: Is it better to use `'` or `"`?

Answer
: {:.fragment} Neither one is better. You will often encounter stylistic choices
like this, so if you don't have a personal preference try to mimic existing
styles.

===

## Assignment

You can expand the vocabulary known to the R interpreter by creating a new
**variable**. Using the symbol `<-` is referred to as assignment: the output of
any command to the right of `<-` gets the name given on its left.

```{r}
x <- seq(0, 100)
```

===

You'll notice that nothing prints to the console, because we assigned the output to a variable.
We can print the value of `x` by evaluating it without assignment.

```{r}
x
```

Assigning values to new variables (to the left of a `<-`) is the only time you
can reference something previously unknown to the interpreter. All other
commands must reference things already in the interpreter's vocabulary.
{:.notes}

===

Once assigned to a variable, a value becomes known to R and you can refer to it in other commands.

```{r}
plot(x, sin(x * 2 * pi / 100))
```

===

The environment is dynamic, but under your control!

- Variables do not persist between sessions (unless loaded from .Rdata)
- Variables only change their value on re-assignment
