---
---

## Parts and Subsets

Any single part of a data structure is always accessible, either by its name or
by its position, using double square brackets: `[[` and `]]`.

===

## Position

```{r}
counts[[1]]
```

```{r}
counts[[3]]
```

===

## Names

Parts of an object may also have a name. The names can be given when you are creating a vector or afterwards using the `names()` function.

===

```{r}
df[['education']]
```

===

```{r title="{{ site.handouts[0] }}"}
names(df) <- c('ed', 'ct')
```

```{r}
df[['ed']]
```

===

Question
: This use of `<-` with `names(x)` on the left is a little odd. What’s going on?

Answer
: {:.fragment} We are overwriting an existing variable, but one that is accessed
through the output of the function on the left rather than the global
environment.

===

For a multi-dimensional array, separate the dimensions within which a part is
requested with a comma.

```{r}
df[[3, 'ed']]
```

It's fine to mix names and indices when selecting parts of an object.
{:.notes}

===

The `$` sign is an additional operator for quick access to a single, named part
of some objects. It's most useful when used interactively with "tab completion" on
the columns of a data frame.

```{r}
df$ed
```

===

## Subsets

Multiple parts of a data structure are similarly accessed using single square
brackets: `[` and `]`. What goes between the brackets, to specify the positions
or names of the desired subset, may be of multiple forms.

===

| Parts     | Result                                            |
|-----------+---------------------------------------------------|
| positives | elements at given positions                       |
| negatives | given positions omitted                           |
| logicals  | elements where the corresponding position is TRUE |
| nothing   | all the elements                                  |

===

```{r title="{{ site.handouts[0] }}"}
days <- c(
  'Sunday', 'Monday', 'Tuesday', 'Wednesday',
  'Thursday', 'Friday', 'Saturday')
weekdays <- days[2:6]
weekend <- days[c(1, 7)]
```

```{r}
weekdays
```

```{r}
weekend
```

===

A logical test applied to a single column produces a vector of `TRUE` and
`FALSE` values that's the right length for subsetting the data.

```{r}
df[df$ed == 'college', ]
```
