---
---

## Base plotting

R has excellent plotting capabilities for many types of graphics.
The `plot()` function is the most basic plotting function, and uses the data provided to determine what kind of plot to make. 

For more advanced plotting such as multi-faceted plots, the libraries [lattice](https://cran.r-project.org/package=lattice) and [ggplot2](https://cran.r-project.org/package=ggplot2) are excellent options. 

===

## Scatterplots

Providing plots with separate "x" and "y" coordinates produces a scatterplot.

```{r title="{{ site.handouts[0] }}"}
plot(animals$hindfoot_length, animals$weight)
```

Using R's formula notation, as in `plot(weight ~ hindfoot_length, data = animals)`, is a more readable syntax for some.

===

## Histograms

To plot binned counts of a single variable, use the `hist` function.

```{r title="{{ site.handouts[0] }}"}
hist(log(animals$weight))
``` 

===

## Boxplots

Use `boxplot` to compare the number of species seen each year.

```{r title="{{ site.handouts[0] }}"}
boxplot(log(weight) ~ year, data = animals)
```
