---
---

## Distributions and Statistics

Since it is designed for statistics, R can easily draw random numbers from statistical distributions and calculate distribution values. 

===

To generate random numbers from a normal distribution, use the function `rnorm()`

```{r title="{{ site.handouts[0] }}"}
samp <- rnorm(n = 10)
```

```{r}
samp
```

===

| Function  | Returns                                      | Notes                     |
|-----------+----------------------------------------------+---------------------------|
| `rnorm()` | Draw random numbers from normal distribution | Specify `n`, `mean`, `sd` |
| `dnorm()` | Probability density at a given number        |                           |
| `pnorm()` | Cumulative probability up to a given number  | left-tailed by default    |
| `qnorm()` | The quantile given a cumulative probability  | opposite of pnorm         |

===

Statistical distributions and their functions.
See *Table 14.1* in **R for Everyone** by Jared Lander for a full table.

| Distribution | Functions     |
|--------------+---------------|
| Normal       | *norm         |
| Binomial     | *binom        |
| Poisson      | *pois         |
| Gamma        | *gamma        |
| Exponential  | *exp          |
| Uniform      | *unif         |
| Logistic     | *logis        |

===

R has built in functions for handling many statistical tests. 

```{r title="{{ site.handouts[0] }}"}
x <- rnorm(n = 100, mean = 25, sd = 7)
y <- rbinom(n = 100, size = 50, prob = .85)
```

```{r}
t.test(x, y)
```

===

Linear regression with the `lm()` function uses a formula notation to specify relationships between variables (e.g. `y ~ x`).

```{r title="{{ site.handouts[0] }}"}
fit <- lm(y ~ x)
```

```{r}
summary(fit)
```

===

## Exercise 8

Recall the formula notation used to plot hindfoot_length against weight for the observations in the `animals` data frame: `plot(hindfoot_length ~ weight, data = animals)`. Instead of the `plot` function, use the `lm` function to estimate the coefficient of `log(weight)` as a predictor of `log(hindfoot_length)`.

[View solution](#solution-8)
{:.notes}
